A tool set for random number generation on GPUs in R

### 2022-01-12 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
p1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3116 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Future work on \pkg{clrng} package could be: (1) Explore other RNGs, for example the MRG32k3a, LFSR113, and Philox-4×32-10 generators in \proglang{clRNG} library, and compare the \proglang{R} performance between using different GPU RNGs. (2) Now that the package can do Cholesky decomposition and matrix multiplication in batches on GPU, which is a motivation for us to work on parallel likelihood evaluations on GPU for Gaussian spatial models in the next step. (3) Create a ``sparse'' matrix class on GPU and use it for simulating Gaussian random fields with sparse correlation structures such as the Gaussian Markov random fields.

>>>>

Some possible future work on \pkg{clrng} package could be: (1) Incorporate other RNGs, for example the MRG32k3a, LFSR113, and Philox-4×32-10 generators from \proglang{clRNG} library, and compare the \proglang{R} performance between using different RNGs on GPU. (2) Create a ``sparse'' matrix class on GPU and use it for simulating Gaussian random fields with sparse correlation structures such as the Gaussian Markov random fields. (3) Apply GPU-generated random numbers in suitable Monte Carlo simulations to speed up the performance.
